Topological Equivariant Artist Model

### 2021-12-29 slides/main.tex
pushed sections
section morphisms
slides up to artist is homset
nt

\begin{frame}{$\mathcal{C}^{op}$ with Objects of \setc}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:2->{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}

@@

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<8-|handout:8->{\dfiberc}
        \onslide*<8-|handout:8->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:3->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3-|handout:3->{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} \& 
            {} \& 
            \onslide*<5-|handout:5->{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<6-|handout:6->{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<2|handout:2>{\opensetc_1 \subset \dbasec}
            \onslide*<3-|handout:3->{\opensetc_1} 
            \onslide*<4-|handout:4->{\arrow[uu, "\sheafc_{\dbasec}", color=sheaf]} 
            \onslide*<6-|handout:6->{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<7-|handout:7->{\arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf]} \& 
            \onslide*<5-|handout:5->{\opensetc_2} 
            \onslide*<5-|handout:5->{\arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:8->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:9>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

@@

\begin{frame}{
\only<-8|handout:-8>{Morphism on Sheaves:}
\only<5-6|handout:5-6>{pullback}\only<7|handout:7>{pushforward} 
\only<8|handout:8>{pullback \& pushforward}\only}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-|handout:7->{\sheafc_{\gbasec}(\gbasec)} 
            \onslide*<7-|handout:7->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-|handout:7->{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbasec)}  \\
            \onslide*<2-|handout:2->{\gbasec}
            \onslide*<3-|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-|handout:7->{\arrow[u, "\sheaf_{\gbasec}", color=sheaf]}
            \onslide*<6,8-|handout:6,8->{\arrow[d, dashed, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1->{\dbasec}
            \onslide*<4-6,8-|handout:4-6,8->{\arrow[d, "\sheaf_{\dbasec}", color=sheaf]}
            \onslide*<7-|handout:7->{\arrow[u, dashed, color=sheaf]} \\
            \onslide*<5-6,8-|handout:5-6,8->{(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec})(\gbasec)} 
            \onslide*<5-6,8-|handout:5-6,8->{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8-|handout:4-6,8->{\sheafc_{\dbasec}(\dbasec)}                             
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{\only<1-3:handout:1-3>{Pullback \& Pushforward are Isomorphic}\only<4-|handout:4>{Data to Graphic is a Sheaf Morphism}}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-|handout:1->{\sheafc_{\gbasec}(\gbasec)} 
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-|handout:1->{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbase)} \\
          \& \& \\
          \onslide*<1-|handout:1->{(\textcolor{functor}{\vindexpull}\sheafc_{\dbase})(\gbasec)}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\gbasec}}", color=homset]} 
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-|handout:1->{\sheafc_{\dbase}(\dbase)} 
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\dbasec}}"', color=homset]}
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:3>{\arrow[lluu, "\textcolor{homset}{hom_{\dbasec,\gbasec}}"' description, dashed, color=homset]}
          \onslide*<4-|handout:4->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

@@

    \begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \textcolor{target}{F(c)} \arrow[dd, "F(f)"', color=target] \arrow[rr, "\alpha_{c}", bend left, color=nattran] \& \textcolor{source}{c} \arrow[dd, "f" description, color=source] \arrow[r, "G"', color=functor] \arrow[l, "F", color=functor] \& \textcolor{target}{G(c)} \arrow[dd, "G(f)", color=target] \\
            {} \arrow[rr, dotted, color=nattran] \& \& {}                      \\
            \textcolor{target}{F(c^{\prime})} \arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran] \& \textcolor{source}{c^{\prime}} \arrow[l, "F"', color=functor] \arrow[r, "G", color=functor] \& \textcolor{target}{G(c^{\prime})}          
        \end{tikzcd}
    \end{equation*}    
    \end{frame}

\begin{comment}

>>>>

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:2->{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}

@@

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<8-|handout:8->{\dfiberc}
        \onslide*<8-|handout:8->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:3->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3-|handout:3->{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} \& 
            {} \& 
            \onslide*<5-|handout:5->{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<6-|handout:6->{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<2|handout:2>{\opensetc_1 \subset \dbasec}
            \onslide*<3-|handout:3->{\opensetc_1} 
            \onslide*<4-|handout:4->{\arrow[uu, "\sheafc_{\dbasec}", color=sheaf]} 
            \onslide*<6-|handout:6->{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<7-|handout:7->{\arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf]} \& 
            \onslide*<5-|handout:5->{\opensetc_2} 
            \onslide*<5-|handout:5->{\arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:8->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:9>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

@@

\begin{frame}{
\only<-8|handout:-8>{Morphism of sheaves:}
\only<5-6|handout:5-6>{pullback}
\only<7|handout:7>{pushforward} 
\only<8,11-|handout:8,11->{pullback \& pushforward}
\only<9|handout:9>{pullback sections}
\only<10|handout:10>{pushforward sections}
}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-8|handout:7-8>{\sheafc_{\gbasec}(\gbasec)} 
            \onslide*<10-|handout:10->{\{\gsectionc: \gbasepointc \scarr \setc \}}
            \onslide*<7-8,10-|handout:7-8,10->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-8|handout:7-8>{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbasec)}  
            \onslide*<10-|handout:10->{(\textcolor{functor}{\vindexpush}\gsectionc:\dbasepointc \scarr \setc)}
            \\
            \onslide*<2-8|handout:2-8>{\gbasec}
            \onslide*<9-|handout:9->{\gbasepointc}
            \onslide*<3-|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-8,10-|handout:7-8,10->{\arrow[u, "\sheaf_{\gbasec}", color=sheaf]}
            \onslide*<6,8-9,11-|handout:6,8-9,11->{\arrow[d, dashed, color=sheaf]} \&  \& 
            \onslide*<1-8|handout:1-8>{\dbasec}
            \onslide*<9-|handout:9->{\dbasepointc}
            \onslide*<4-6,8-9,11-|handout:4-6,8-9,11->{\arrow[d, "\sheaf_{\dbasec}", color=sheaf]}
            \onslide*<7-8,10-|handout:7-8,10->{\arrow[u, dashed, color=sheaf]} \\
            \onslide*<5-6,8|handout:5-6,8>{(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec})(\gbasec)} 
            \onslide*<9,11-|handout:9,11->{\{\textcolor{functor}{\vindexpull}\dsectionc:\gbasepointc\scarr\setc\}}
            \onslide*<5-6,8-9,11-|handout:5-6,8-9,11->{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8|handout:4-6,8>{\sheafc_{\dbasec}(\dbasec)}                      
            \onslide*<9,11-|handout:9,11->{\{\dsectionc: \dbasepointc \scarr \setc \}}
        \end{tikzcd}
    \end{equation*}
    \onslide<9,11-|handout:9,11->{
        \begin{equation*}
            \dsectionc^{\textcolor{functor}{*}}(\gbasepointc) = \dsectionc(\textcolor{functor}{\vindex}(\gbasepointc)) = \dsectionc(\dbasepointc)
        \end{equation*}
    }
    \onslide<10-|handout:10,11->{
        \begin{equation*}
            \gsectionc(\gbasepointc) = \gsectionc_{\textcolor{functor}{*}}(\dbasepointc) = \gsectionc(\textcolor{functor}{\vindexpre}(\dbasepointc))
        \end{equation*}
    }
\end{frame}

\begin{frame}{
    \only<1-3|handout:1-3>{Pullback \& Pushforward are Isomorphic}
    \only<4|handout:4>{$\vartistc:\sheafc_{\dbasec}\rightarrow \sheafc_{\gbasec}$}
    \only<5-|handout:5->{$\vartistc: \dsectionc \mapsto \gsectionc$}
    }
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-4|handout:1-4>{\sheafc_{\gbasec}(\gbasec)} 
          \onslide*<5-|handout:5->{\{\gsectionc:\gbasepointc \scarr \setc\}}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-4|handout:1-4>{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbase)}
          \onslide*<5-|handout:5>{\{\vindexpushc \gsectionc: \dbasepointc \scarr\setc\}}
          \\
          \& \& \\
          \onslide*<1-4|handout:1-4>{(\textcolor{functor}{\vindexpull}\sheafc_{\dbase})(\gbasec)}
          \onslide*<5-|handout:5>{\{ \vindexpullc\dsectionc:\gbasepointc\scarr \setc\}}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\gbasec}}", color=homset]} 
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-4|handout:1-4>{\sheafc_{\dbase}(\dbase)} 
          \onslide*<5-|handout:5->{\{\dsectionc:\dbasepointc \scarr \setc\}}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\dbasec}}"', color=homset]}
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:3>{\arrow[lluu, "\textcolor{homset}{hom_{\dbasec,\gbasec}}"' description, dashed, color=homset]}
          \onslide*<4-|handout:4->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

@@

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:2->{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:2->{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:4-5>{\arrow[rr, "\alpha_{c}", bend left, color=nattran]}  
            \onslide*<6|handout:6>{\arrow[rr, "\alpha_{c}", color=nattran]} \& 
            \onslide*<1-4|handout:1-4>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1-4>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:3-4>{\arrow[r, "G"', color=functor]}
            \onslide*<2-4|handout:2-4>{\arrow[l, "F", color=functor]} \& 
            \onslide*<3-|handout:3->{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:3->{\arrow[dd, "G(f)", color=target]} \\
            {} 
            \onslide*<4|handout:4>{\arrow[rr, dotted, color=nattran]}
            \onslide*<5|handout:5>{\arrow[rr, color=nattran]} \& \& {}                      \\
            \onslide*<2-|handout:2->{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:4-5>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran]} 
            \onslide*<4-5|handout:6>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran]}\& 
            \onslide*<1-4|handout:1-4>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:2-4>{\arrow[l, "F"', color=functor]} 
            \onslide*<3-4|handout:3-4>{\arrow[r, "G", color=functor]} \& 
            \onslide*<3-|handout:3->{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}    
\end{frame}

\begin{frame}{$\vartist_{\vindexpullc}: \vindexpullc\sheafc_{\dbasec} \rightarrow \sheafc_{\gbasec}$}

\end{frame}
\begin{comment}
